---
title: "Exploratory Data Analysis"
description: |
  The site provides a collection of resources and summary reports containing statistics and other relevant information about the datasets.
---

```{r, setup, include = FALSE}
knitr::opts_chunk$set(echo=FALSE)

# Common functions
library(reportlib)
r_func_path <- "./_func"
```

## Regional Summary Reports

  * [Arctic Ocean Summary Report](https://aiqc-hub.github.io/arc-report/)
  * [Baltic Sea Summary Report](https://aiqc-hub.github.io/bal-report/)
  * [Mediterranean Sea Summary Report](https://aiqc-hub.github.io/med-report/)

---

## Original NetCDF Datasets
```{r, eda_netcdf, child = file.path(r_func_path, "eda_netcdf.Rmd")}
```

---

## Exported Parquet Datasets
```{r, eda_parquet, child = file.path(r_func_path, "eda_parquet.Rmd")}
```

---

## Duplicate Profiles and NRT vs CORA

Both analyses are part of the `ctddump` pipeline that writes the Parquet files, and its own
reports carry them for the current export rather than repeating the numbers here:

  * [ctddump: CTD data summary reports](https://aiqc-hub.github.io/ctddump-report-example/index.html)

There is one report per region and product. **Deduplication** counts the profiles that repeat
within a platform and across platforms; **Comparison** matches a near-real-time product against
CORA and GL and reports how much of their platform and profile coverage overlaps. Each report
also shows the source files it read, the counts after conversion to Parquet, and the cleaning
stages that precede both analyses.

---

## Fraction of QC4 Flags per Profile
```{r, eda_qc4_fraction, child = file.path(r_func_path, "eda_qc4_fraction.Rmd")}
```

---

## Distributions of QC 1 & 4 Flags Over Time
```{r, eda_qc_over_time, child = file.path(r_func_path, "eda_qc_over_time.Rmd")}
```

---
