### Detection criteria

::: {.panelset}
::: {.panel}

#### Strict criteria

The following variables must match:

 - Platform (`platform_code`)
 - Timestamp (`profile_timestamp`)
 - Truncated longitude (`round(longitude, 3)`)
 - Truncated latitude (`round(latitude, 3)`)
 - Number of observations per profile

:::

::: {.panel}

#### Relaxed criteria

The following variables must match:

 - Platform (`platform_code`)
 - Timestamp (`profile_timestamp`)
 - Truncated longitude (`round(longitude)`)
 - Truncated latitude (`round(latitude)`)

:::
:::

### Number of matched profiles

::: {.panelset}
::: {.panel}

#### Arctic Ocean

```{r, t_nrt_vs_core_arc, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("NRT (AR) vs CORA", "NRT (GL) vs CORA"),
                 `# Profiles` = c(297876, 207372),
                 `# Strict criteria` = c(60368,  96228),
                 `Strict (%)` = c("20.27%", "46.4%"),
                 `# Relaxed criteria` = c(67009, 110731),
                 `Relaxed (%)` = c("22.5%", "53.4%"))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::

::: {.panel}

#### Baltic Sea

```{r, t_nrt_vs_core_bal, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("NRT (BO) vs CORA", "NRT (GL) vs CORA"),
                 `# Profiles` = c(107063, 6699),
                 `# Strict criteria` = c(80788,  1685),
                 `Strict (%)` = c("75.46%", "25.15%"),
                 `# Relaxed criteria` = c(97395, 1910),
                 `Relaxed (%)` = c("90.97%", "28.51%"))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::

::: {.panel}

#### Mediterranean Sea

```{r, t_nrt_vs_core_med, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("NRT (MO) vs CORA", "NRT (GL) vs CORA"),
                 `# Profiles` = c(1633, 96728),
                 `# Strict criteria` = c(136,  31276),
                 `Strict (%)` = c("8.33%", "32.33%"),
                 `# Relaxed criteria` = c(289, 40247),
                 `Relaxed (%)` = c("17.7%", "41.61%"))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::
:::
