::: {.panel-tabset}

### Arctic Ocean

#### Data ID

  * **AR** & **GL**: [cmems_obs-ins_arc_phybgcwav_mynrt_na_irr](https://doi.org/10.48670/moi-00031)
  * **CORA**: [cmems_obs-ins_glo_phy-temp-sal_my_cora_irr](https://data.marine.copernicus.eu/product/INSITU_GLO_PHY_TS_DISCRETE_MY_013_001)

#### Number of files

```{r, t_netcdf_arc, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("AR", "GL", "CORA"),
                 `# Files` = c(204, 560, 20975),
                 `# Files with TEMP` = c(203, 552, 20975),
                 `# Files with PSAL` = c(194, 552, 20963),
                 `# Files with PRES` = c(202, 350, 17402),
                 `# Files with DEPH` = c(2, 380, 20817),
                 `# Files with Time QC` = c(204, 560, 20975),
                 `# Files with Position QC` = c(195, 560, 20975))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

### Baltic Sea

#### Data ID

  * **BO**: [cmems_obs-ins_bal_phybgcwav_mynrt_na_irr](https://doi.org/10.48670/moi-00032)
  * **CORA**: [cmems_obs-ins_glo_phy-temp-sal_my_cora_irr](https://data.marine.copernicus.eu/product/INSITU_GLO_PHY_TS_DISCRETE_MY_013_001)
 

#### Number of files
  
```{r, t_netcdf_bal, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("BO", "CORA"),
                 `# Files` = c(753, 12482),
                 `# Files with TEMP` = c(753, 12482),
                 `# Files with PSAL` = c(753, 12482),
                 `# Files with PRES` = c(576, 12473),
                 `# Files with DEPH` = c(177, 11973),
                 `# Files with Time QC` = c(753, 12482),
                 `# Files with Position QC` = c(461, 12482))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

### Mediterranean Sea

#### Data ID

  * **MO** & **GL**: [cmems_obs-ins_med_phybgcwav_mynrt_na_irr](https://doi.org/10.48670/moi-00044)
  * **CORA**: [cmems_obs-ins_glo_phy-temp-sal_my_cora_irr](https://data.marine.copernicus.eu/product/INSITU_GLO_PHY_TS_DISCRETE_MY_013_001)

#### Number of files

```{r, t_netcdf_med, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("MO", "GL", "CORA"),
                 `# Files` = c(79, 187, 7905),
                 `# Files with TEMP` = c(47, 185, 7905),
                 `# Files with PSAL` = c(79, 179, 7904),
                 `# Files with PRES` = c(79, 114, 7849),
                 `# Files with DEPH` = c(1, 155, 7869),
                 `# Files with Time QC` = c(79, 187, 7905),
                 `# Files with Position QC` = c(79, 186, 7905))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::
